%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Software Engineer and Mobile Developer} % Job title
    {NCR CORPORATION} % Organization
    {NCR Corporation, Hyderabad} % Location
    {July. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {My responsibilities include developing both iOS and Android native apps for the clients of NCR.}
        \item {Worked with 4 Projects (Android/iOS) in 5 months.}
        \item {Technologies: JAVA, Objective C, REST API, XML.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Android Developer (Freelanced Project)} % Job title
    {Stumagz Android Application (10K Downloads @recognized in FORBES ASIA UNDER30)} % Organization
    {Hyderabad} % Location
    {Jun. 2017 - July. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented RESTful API client for student magazine application Stumagz.}
        \item {Built rest client using retrofit. Glide for image loading, GSON for Json parsing, Other Java features like AsynTask, Threading to achieve asynchronous API calls.}
        \item {AppLink: https://play.google.com/store/apps/details?id=com.tdevelopers.stumagz.\newline}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder \& Developer} % Job title
    {Questo (Major Project)} % Organization
    {Hyderabad} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Questo is crowd sourced application, in which an authenticated user can upload a MCQ or write a blog/feed with tags included.}
        \item {Implemented  using Firebase Cloud, FirebaseDB, NoSQL, Facebook Login, Google Cloud Storage, Firebase Cloud Messaging.}
        \item {Play Store Link: https://play.google.com/store/apps/details?id=com.tdevelopers.questo
       \item Github Link: https://github.com/saitejdandge/Questo-Android-Application}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer} % Job title
    {Disease Diagonsis based on symptoms using machine learning (Major Project)} % Organization
    {Hyderabad} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a algorithm that works on supervised Learning pattern by taking exsisting data and diagnose disease based on symptoms.}
        \item {Implemented  using Google Tensor Flow Python Library.
        Classifier: Decision Tree Classifier, Convolutional Neural Network.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Google Facilitator for Applied CS with Android Programme, CBIT} % Job title
    {Google} % Organization
    {CBIT, Hyderabad} % Location
    {March. 2016 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Delivered workshops on Android Development, Data Structures, Algorithms to students in my campus in regard of this programme.}
        \item {Talked about latest trending topics like Firebase Cloud, AWS, Machine Learning(TensorFlow), Implementation of Data Structures in Android.}
        \item {More than 200 people participated in this programme. Workshop benefited students won 7 national rank in Smart Hackathon under supervision of Mr.Narendra Modi, Government of India.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Founder \& Developer} % Job title
    {Track My Bus, Android Application (In progress)} % Organization
    {Hyderabad} % Location
    {December - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This application is an effort to solve problem of tracking real time bus positions of my college and users get push notification when event occurs.}
        \item {Used serverless Architecture. AWS Lambda}
        \item{
        Technologies: Amazon DynamoDb, AWS Lambda, Google Map API, Google Places API.}\item{
        Github Link: https://github.com/saitejdandge/NewApplication
        }
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }


  \cventry
    {Developer} % Job title
    {Noter (Web Application)} % Organization
    {Hyderabad} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Simple Web application built using Angular 2, Mongo DB, Firebase Hosting.}
        \item {Built API using NodeJS to fetch data from MongoDB hosted in cloud. UI built using Angular material.}
        \item{
        Front End- Angular 2\newline
Back End- Mongo Rest API calls (Reference : http://docs.mlab.com/data-api)\newline
Database - Mongo DB\newline
Hosting - Firebase Hosting.
        }
        \item{
        Live running at: https://noter-4e3e3.firebaseapp.com/notes}\item{
        Github Link: https://github.com/saitejdandge/Noter-using-MongoDB-Angular2-NodeJS-}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
  \cventry
    {Developer} % Job title
    {Hide My Text (Cryptic Tool in Android)} % Organization
    {Hyderabad} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This app provides secret messaging using poly-alphabetic cipher symmetric encryption which is unique for every pair of chat.}
        \item{
        Play Store Link: https://play.google.com/store/apps/details?id=com.tdevelopers.hidemyttext}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
\end{cventries}
